\vspace{-10mm}\bf \mytitle

### 2022-11-21 ms.Rnw
update for pomp 4.3.4.2

<<debug,echo=F>>=
# run_level <- "jasa-sept-2020"
 run_level <- "manual"
# run_level <- 2

@@

<<bm_kf,cache=F,echo=F>>=
bm_kf <- stew(file=paste0(bm_files_dir,"bm_kf.rda"),seed=25487,{
  foreach(i=seq_along(bm_U),.combine=c)%do%{
    bm <- bm_list[[i]]
    bm_units <- bm_U[i]
    bm_dist <- function(u,v,U) min(abs(u-v),abs(u-v+U),abs(u-v-U))
    bm_dmat <- matrix(0,bm_units,bm_units)
    for(u in 1:bm_units) {
      for(v in 1:bm_units) {
        bm_dmat[u,v] <- bm_dist(u,v,bm_units)
      }
    }
    rootQ <- coef(bm)["rho"]^bm_dmat * coef(bm)["sigma"]
    kf <- pomp:::kalmanFilter(
      t=1:bm_N,
      y=obs(bm),
      X0=rinit(bm),
      A= diag(bm_units),
      Q= rootQ %*% rootQ,
      C=diag(bm_units),
      R=diag(coef(bm)["tau"]^2, nrow=bm_units)
    )$loglik
  } -> bm_kf_results
})

@@

slice_abf_mcap <- mcap(
  lp=slice_abf_results[,"logLik"],
  parameter=slice_abf_results[,"g"],
  lambda = 1
)

slice_ubf_mcap <- mcap(
  lp=slice_ubf_results[,"logLik"],
  parameter=slice_ubf_results[,"g"],
  lambda = 0.8
)

slice_bpf_mcap <- mcap(
  lp=slice_bpf_results[,"logLik"],
  parameter=slice_bpf_results[,"g"],
  lambda = 1
)

slice_enkf_mcap <- mcap(
  lp=slice_enkf_results[,"logLik"],
  parameter=slice_enkf_results[,"g"],
  lambda = 1
)

plot.profile2 <- function(mcap1,ylab,xline=2.5,yline=2.5,xlab="",quadratic=FALSE,...){
  if(missing(ylab)) ylab <- "log likelihood"
  # par(mai=c(0.7,0.7,0.3,0.3))
  ggplot() + geom_point(aes(x = mcap1$parameter, y = mcap1$lp)) + 
    geom_line(mapping = aes(x = mcap1$fit$parameter, y = mcap1$fit$smoothed),
              color = "red") +
    {if(quadratic) geom_line(mapping = aes(x = mcap1$fit$parameter, y = mcap1$fit$quadratic),
                             color = "blue",
                             lwd = 1.25)} +
    labs(x = xlab, y = ylab) +
    geom_vline(xintercept = mcap1$ci, color = "red") + 
    geom_hline(yintercept = max(mcap1$fit$smoothed, na.rm = T) - mcap1$delta, color = "red") +
    theme(panel.border = element_rect(colour = "black", fill=NA))
  }

@@

plot.profile <- function(mcap1,ylab,xline=2.5,yline=2.5,xlab="",...){
  if(missing(ylab)) ylab <- "log likelihood"
  plot(mcap1$lp ~ mcap1$parameter, xlab="",ylab="",xaxt="n",...)
  mtext(side=2,text=ylab,line=yline)
  mtext(side=1,text=xlab,line=yline)
  lines(mcap1$fit$parameter,mcap1$fit$smoothed, col = "red", lwd = 1.5)
  abline(v=mcap1$ci,col="red")
  abline(h=max(mcap1$fit$smoothed,na.rm=T)-mcap1$delta,col="red")
}

@@

yloc <- 0.05; xloc <- 570
mtext("A",side=2,line=2.5,las=1,padj=-4,cex=1.8)
text(xloc,
  (1-yloc)*min(slice_abf_mcap$lp) + yloc*max(slice_abf_mcap$lp),
  cex=1.4,"ABF")

@@

mtext("B",side=2,line=2.5,las=1,padj=-4,cex=1.8)
text(xloc,
  (1-yloc)*min(slice_bpf_mcap$lp) + yloc*max(slice_bpf_mcap$lp),
  cex=1.4,"BPF")

@@

mtext("C",side=2,line=2.5,las=1,padj=-4,cex=1.8)
mtext("G",side=1,line=2.5)
text(xloc,
  (1-yloc)*min(slice_enkf_mcap$lp) + yloc*max(slice_enkf_mcap$lp),
  cex=1.4,"EnKF")

@@

plot.profile <- function(mcap1,ylab,xline=2.5,yline=2.5,xlab="",quadratic=FALSE,...){
   if(missing(ylab)) ylab <- "profile log likelihood"
   ggplot() + geom_point(aes(x = mcap1$parameter, y = mcap1$lp), shape = 1) +
      geom_line(mapping = aes(x = mcap1$fit$parameter, y = mcap1$fit$smoothed),
                color = "red") +
      {if(quadratic) geom_line(mapping = aes(x = mcap1$fit$parameter, y = mcap1$fit$quadratic),
                               color = "blue",
                               lwd = 1.25)} +
      labs(x = xlab, y = ylab) +
      geom_vline(xintercept = mcap1$ci, color = "red") +
      geom_hline(yintercept = max(mcap1$fit$smoothed, na.rm = T) - mcap1$delta, color = "red") +
      theme(panel.border = element_rect(colour = "black", fill=NA))
}
g_prof %>% dplyr::group_by(g) %>% dplyr::filter(loglik==min(loglik)) -> mins
g_prof[which(!(g_prof$loglik %in% mins$loglik)),] -> top_g_prof

g_prof_mcap <- spatPomp::mcap(
   lp=top_g_prof[,"loglik"],
   parameter=top_g_prof[,"g"],
   lambda = 0.90
)
plot.profile(g_prof_mcap,xlab='G', quadratic = FALSE) +
   geom_vline(xintercept=400,color="blue",linetype="dashed") +
   theme(axis.text.x = element_text(size = 12),
         axis.text.y = element_text(size = 12),
         axis.title.x = element_text(size = 14),
         axis.title.y = element_text(size = 14),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank(),
         panel.border = element_rect(colour = "black", fill=NA, size=0.8),
         axis.line = element_line(colour = "black"))

>>>>

<<debug,echo=F>>=
# run_level <- "jasa-sept-2020"
# run_level <- "manual"
 run_level <- 1

@@

<<bm_kf,cache=F,echo=F>>=
bm_kf <- stew(file=paste0(bm_files_dir,"bm_kf.rda"),seed=25487,{
  foreach(i=seq_along(bm_U),.combine=c)%do%{
    bm <- bm_list[[i]]
    bm_units <- bm_U[i]
    bm_dist <- function(u,v,U) min(abs(u-v),abs(u-v+U),abs(u-v-U))
    bm_dmat <- matrix(0,bm_units,bm_units)
    for(u in 1:bm_units) {
      for(v in 1:bm_units) {
        bm_dmat[u,v] <- bm_dist(u,v,bm_units)
      }
    }
    rootQ <- coef(bm)["rho"]^bm_dmat * coef(bm)["sigma"]
    kf <- pomp:::kalmanFilter(bm,
      X0=rinit(bm),
      A= diag(bm_units),
      Q= rootQ %*% rootQ,
      C=diag(bm_units),
      R=diag(coef(bm)["tau"]^2, nrow=bm_units)
    )$logLik
  } -> bm_kf_results
})

@@

slice_abf_mcap <- mcap(
  logLik=slice_abf_results[,"logLik"],
  parameter=slice_abf_results[,"g"],
  span = 1
)

slice_ubf_mcap <- mcap(
  logLik=slice_ubf_results[,"logLik"],
  parameter=slice_ubf_results[,"g"],
  span = 0.8
)

slice_bpf_mcap <- mcap(
  logLik=slice_bpf_results[,"logLik"],
  parameter=slice_bpf_results[,"g"],
  span = 1
)

slice_enkf_mcap <- mcap(
  logLik=slice_enkf_results[,"logLik"],
  parameter=slice_enkf_results[,"g"],
  span = 1
)

plot.profile2 <- function(mcap1,ylab,xline=2.5,yline=2.5,xlab="",quadratic=FALSE,...){
  if(missing(ylab)) ylab <- "log likelihood"
  # par(mai=c(0.7,0.7,0.3,0.3))
  ggplot() + geom_point(aes(x = mcap1$parameter, y = mcap1$logLik)) + 
    geom_line(mapping = aes(x = mcap1$fit$parameter, y = mcap1$fit$smoothed),
              color = "red") +
    {if(quadratic) geom_line(mapping = aes(x = mcap1$fit$parameter, y = mcap1$fit$quadratic),
                             color = "blue",
                             lwd = 1.25)} +
    labs(x = xlab, y = ylab) +
    geom_vline(xintercept = mcap1$ci, color = "red") + 
    geom_hline(yintercept = max(mcap1$fit$smoothed, na.rm = T) - mcap1$delta, color = "red") +
    theme(panel.border = element_rect(colour = "black", fill=NA))
  }

@@

plot.profile <- function(mcap1,ylab,xline=2.5,yline=2.5,xlab="",...){
  if(missing(ylab)) ylab <- "log likelihood"
  plot(mcap1$logLik ~ mcap1$parameter, xlab="",ylab="",xaxt="n",...)
  mtext(side=2,text=ylab,line=yline)
  mtext(side=1,text=xlab,line=yline)
  lines(mcap1$fit$parameter,mcap1$fit$smoothed, col = "red", lwd = 1.5)
  abline(v=mcap1$ci,col="red")
  abline(h=max(mcap1$fit$smoothed,na.rm=T)-mcap1$delta,col="red")
}

@@

yloc <- 0.05; xloc <- 570
mtext("A",side=2,line=2.5,las=1,padj=-4,cex=1.8)
text(xloc,
  (1-yloc)*min(slice_abf_mcap$logLik) + yloc*max(slice_abf_mcap$logLik),
  cex=1.4,"ABF")

@@

mtext("B",side=2,line=2.5,las=1,padj=-4,cex=1.8)
text(xloc,
  (1-yloc)*min(slice_bpf_mcap$logLik) + yloc*max(slice_bpf_mcap$logLik),
  cex=1.4,"BPF")

@@

mtext("C",side=2,line=2.5,las=1,padj=-4,cex=1.8)
mtext("G",side=1,line=2.5)
text(xloc,
  (1-yloc)*min(slice_enkf_mcap$logLik) + yloc*max(slice_enkf_mcap$logLik),
  cex=1.4,"EnKF")

@@

plot.profile <- function(mcap1,ylab,xline=2.5,yline=2.5,xlab="",quadratic=FALSE,...){
   if(missing(ylab)) ylab <- "profile log likelihood"
   ggplot() + geom_point(aes(x = mcap1$parameter, y = mcap1$logLik), shape = 1) +
      geom_line(mapping = aes(x = mcap1$fit$parameter, y = mcap1$fit$smoothed),
                color = "red") +
      {if(quadratic) geom_line(mapping = aes(x = mcap1$fit$parameter, y = mcap1$fit$quadratic),
                               color = "blue",
                               lwd = 1.25)} +
      labs(x = xlab, y = ylab) +
      geom_vline(xintercept = mcap1$ci, color = "red") +
      geom_hline(yintercept = max(mcap1$fit$smoothed, na.rm = T) - mcap1$delta, color = "red") +
      theme(panel.border = element_rect(colour = "black", fill=NA))
}
g_prof %>% dplyr::group_by(g) %>% dplyr::filter(loglik==min(loglik)) -> mins
g_prof[which(!(g_prof$loglik %in% mins$loglik)),] -> top_g_prof

g_prof_mcap <- pomp::mcap(
   logLik=top_g_prof[,"loglik"],
   parameter=top_g_prof[,"g"],
   span = 0.90
)
plot.profile(g_prof_mcap,xlab='G', quadratic = FALSE) +
   geom_vline(xintercept=400,color="blue",linetype="dashed") +
   theme(axis.text.x = element_text(size = 12),
         axis.text.y = element_text(size = 12),
         axis.title.x = element_text(size = 14),
         axis.title.y = element_text(size = 14),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank(),
         panel.border = element_rect(colour = "black", fill=NA, size=0.8),
         axis.line = element_line(colour = "black"))
